---
title: "Homework 5"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(viridis)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

### Import CSV

```{r import_data}
hom_df =
  read_csv("./data/homicide-data.csv")
```

### Raw Data Description

```{r skim, include = FALSE}
skimr::skim(hom_df)
```

The data contains `r nrow(hom_df)` observations and `r ncol(hom_df)` variables. For each reported case of homicide, it provides victim's name, race, age, sex, location (city, state, latitude, and longitude), and disposition.

### Number of Homicides and Unsolved Cases in Each City

Following steps were taken to find the total number of homicides and unsolved cases in each city:
1. Created a new variable called "city_state"
2. Removed invalid data ("Tulsa, AL")
3. Created a data frame that summarizes the total # of homicide cases in each city
4. Created a data frame that summarizes the total # of unsolved cases in each city
5. Merged the two data frames
6. Printed a table with a summary of # of homicide and unsolved cases in each city

```{r org_data}
hom_df = hom_df %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  filter(city_state !="Tulsa, AL")

homicide = hom_df %>% 
  group_by(city_state) %>% 
  summarize(total = n())

unsolved = hom_df %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(unsolved = n())

summ = left_join(homicide, unsolved, by = "city_state") 
knitr::kable(summ)
```

### Baltimore, MD: Proportion of Unsolved Homicide Cases

To find the propotion of unsolved cases in Baltimore MD,
1. Filtered the dataset created in previous step so only information for Baltimore, MD is included
2. Used `prop.test` and `broom::tidy` to find test proporitons

```{r MD_unsolved}
MD_unsolved = summ %>% 
  filter(city_state == "Baltimore, MD")

MD_prop = prop.test(MD_unsolved %>%  pull(unsolved), MD_unsolved %>% pull(total)) %>% 
  broom::tidy()

MD_prop
```

64.6% (95% CI: 62.8%, 66.3%) of reported homicides in Baltimore, MD are unsolved cases.

### Proportion of Unsolved Cases in Each City
To generate a data frame that provides proportion of unsolved cases in each city
1. Created a function (prop_fx1) that can be used for iteration
2. Applied the function to the summ data frame which was created earlier

```{r function,iteration}
prop_fx1 = function(x_unsolved, n_total) {

prop_fx2 = 
  prop.test(
    x = x_unsolved, n = n_total, 
    p = NULL, alternative = c("two.sided", "less", "greater"), 
    conf.level = .95, 
    correct = TRUE) %>% 
  broom::tidy() %>%
    select(estimate, conf.low, conf.high)

prop_fx2
}

city_summ = summ %>% 
  mutate(
    prop_unsolved = 
      map2(.x = unsolved, .y = total, ~prop_fx1(x = .x, n = .y))) %>% 
  unnest(prop_unsolved)

city_summ
```

### Plot

```{r ggplot}
plot = city_summ %>% 
  ggplot(aes(x = fct_reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Unsolved Homicide Cases in the United States",
    x = "Location (city, state)", 
    y = "Proportion of Unsolved Cases"
    ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust = 1))

print(plot)
```

## Problem 3

### Simulation 

```{r element}
sim_fx = function(n_obs = 30, mu = 0, sigma = 5){
  sim_data =
    tibble(x = rnorm(n = n_obs, mean = mu, sd = sigma))

sim_data %>% summarize(
  mu_hat = mean(x),
  p_value = t.test(x, conf.level = .95)$p.value)
}

mu = 0
output_lists = map(.x = mu, ~rerun(5000, sim_fx(mu = .x)))
```

### Repeating for different mu's

```{r 5000}
sim_df =
  tibble(mu = c(1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mu, ~rerun(5000, sim_fx(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  mutate(reject = ifelse(p_value < .5, 'reject', 'fail to reject'))
```

### Plots

```{r plots}
plot1 = sim_df %>% 
  ggplot(aes(x = mu, fill = reject)) +
  geom_bar(position = "fill") +
  lab(x = "mu", y = "% rejected")

plot1

plot2 = sim_df %>% 
  group_by(mu) %>% 
  summarize(vars(mu_hat), list(mu_est = mean)) %>% 
  ggplot(aes(x = mu, y = mu_est)) +
  geom_point() +
  lab( x = "mu", y = "mu_hat estimate")

plot3 = sim_df %>% 
  filter(reject == 'reject') %>% 
  group_by(mu) %>% 
  summrize(vars(mu_hat), list(n_mean = mean)) %>% 
  ggplot(aes(x = mu, y = n_mean)) +
  geom_point() +
  labs(x = "true mu", y = "sample mean")
  
```


